References

### 2017-04-25 cv/CoverLetter/Eurex.tex

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Cross Asset Quantitative Analysis team}{Citi}{London}
\date{\today}
\opening{Dear Sir/Madam,}
\closing{Best Regards,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
% \enclosure[Attached]{curriculum vit\ae{}, Master's thesis in
%   Econophysics}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I see on Citi's website that you are recruiting a quantitative
analyst to join your cross asset quantitative analysis team. In the
description of the job, you emphasise knowledge and skills in time
series analysis, C++ programming and understanding of the financial
market, which are indeed areas that I know well and am passionate
about. So I would like to ask you for your consideration.

I am currently a PhD student at Copenhagen University, researching in
Mathematical statistics and particularly in time series analysis,
extreme value theory and random matrix theory. I will be available for
full-time work on 1st July 2017. I expect to receive my degree on 30th
September, 2017. So far I have co-authored and published two papers on
eigen systems of sample covariance matrices, with a focus on
heavy-tailed (e.g. power-law tail) time series. These results are
applicable to principle component analysis, for example.

I am also finalising two other papers. One of them is about how an
investor's preference (as quantified by {\em Generalised
  Disappointment Aversion}) of an equity varies with the tail
parameters of the stationary distribution of the equity. This
result can be applied to, for example, portfolio construction and
assessment of the overall market risk. As part of the paper, I have
also done statistical analysis on the tail parameters of equities in
the S\&P 500 index, specifically the ``Energy'', ``Consumer Staples''
and ``Information Technology'' sectors. R and C++ programming are
indispensable part of the work.

The fourth paper of mine is about estimation of the probability of very
large losses posed by portfolios whose volatility dynamics are
time series modelled by univariate GARCH(p,q) or multivariate
GARCH processes. Because the stationary distribution of such a process
is not known exactly, the aforementioned probability as well as the
related risk measures {\em Value at Risk} and {\em Expected
  Shortfall} cannot be computed precisely. In the paper I propose 
an estimator based on importance sampling and Markov chain theory and
naturally, would be more than happy to see it applied in practical
risk management. I have implemented the estimator in C++, and in
particular, have used the OpenMP directives to achieve high
performance via parallel computing.

Citi is a great investment bank that I have known since my
childhood. I know taking a role in this esteemed organisation presents
many challenges and opportunities. Through constant endeavour towards
ever greater excellence, I hope to develop a productive career that I
will be proud of by contributing my part to the success of Citi.

>>>>

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
% \recipient{Cross Asset Quantitative Analysis team}{Citi}{London}
\recipient{Deutsche B\"orse Group}{Frankfurt am Main}{Germany}
\date{\today}
\opening{Dear Sir/Madam,}
\closing{Best Regards,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
% \enclosure[Attached]{curriculum vit\ae{}, Master's thesis in
%   Econophysics}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I see on {\em Monster} that you are recruiting a quantitative risk
analyst to join your team of {\em Risk methodology and New products}.
From your description of the responsibilities and requirements, I
understand you are looking for someone who is strong both in
statistical analysis and in software development using Matlab, C++ and
SQL.

As is detailed in my CV, I am anticipating to get my PhD in {\em
  Mathematical Statistics} from Copenhagen University this September
and have co-authored 2 papers on the eigen systems of sample
covariance matrices of heavy tailed time series. At the time of
writing, I am also finalizing two other papers, one about tail
parameters of equity returns and the other about estimation of
the probabilities of large losses by importance sampling.
These results are applicable to principle component analysis,
portfolio optimization as well as risk management; and indeed, I am
keen to apply them and see them making a real impact on business.

Speaking about the application of mathematical models, I think my past
experience as a software developer is worth mentioning. As is detailed
in my CV, I worked as a software developer for 6.5 years in several
companies and accumulated abundant experience in C, C++, R, Matlab
programming as well as in data analysis and algorithm implementation.
Thus I am confident to take on the challenges of a quantitative risk
analyst at {\em Eurex}.

### 2017-04-25 cv/References.tex
Added CV and cover letters.

My recommenders are:
\begin{itemize}
\item Sven \AA berg, professor and Head of Mathematical Physics at
  Lund University
\item Ferdi Aryasetiawan, professor of Mathematical Physics at
  Lund University
\end{itemize}

>>>>

I would like to refer you to the following contacts for references of
my education and employment.
\begin{itemize}
\item Thomas Mikosch, {\em professor of Mathematics at Copenhagen
    University}, my PhD supervisor
  \begin{itemize}
  \item Email: mikosch@math.ku.dk
  \item Office phone: +45 353 30414
  \end{itemize}
\item Sven \AA berg, {\em professor and Head of Mathematical Physics
    at Lund University}, my Master thesis supervisor
  \begin{itemize}
  \item Email: sven.aberg@matfys.lth.se
  \item Office phone: +46 46 222 96 33
  \item Mobile phone: +46 70 557 35 69
  \end{itemize}
\item Ferdi Aryasetiawan, {\em professor of Mathematical Physics at
    Lund University}, my teacher of multiple courses
  \begin{itemize}
  \item Email: ferdi.aryasetiawan@teorfys.lu.se
  \item Office phone: +46 46 222 90 89
  \end{itemize}
\item Fredrik l\"of, {\em Technical Project Manager and Team Leader at
    Bombardier Transportation}, my supervisor at ST-Ericsson
  \begin{itemize}
  \item Email: fredrik.n.lof@gmail.com
  \item LinkedIn: https://www.linkedin.com/in/fredrik-lof/
  \end{itemize}
\end{itemize}
